---
title: <span style="text-decoration:underline">Portfolio Analysis</span>
author: "Manik Hindwan"
date: "26 May 2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
    
```{r echo = FALSE}
htmltools::img(src ="https://www.snaptest.org/mobile/img/clglogos/scmhrd.png", 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; width:125px ; height:125px;')
```

<p><h4> <b>Below is the analysis of a portfolio consisting of 10 stocks. The weights used in the analysis have been calculated as:</b> Individual Stock's value/Total value of the portfolio</h4></p> 
 
```{r include= FALSE}
library(quantmod)
library(dygraphs)
library(TTR)
library(tseries)
library(Quandl)
library(PerformanceAnalytics)
library(dplyr)
library(tidyverse)
library(RColorBrewer)

```

<p>&nbsp;</p>

The stocks used in the portfolio are <span style="color:red">ABB, Bank of Baroda, Crompton Greaves, Dabur, ITC, Nestle India, ONGC, TCS, Reliance Industries Ltd and Pfizer</span>, 
trading in the <span style="color:blue">NSE</span>.

```{r include=FALSE, message = FALSE}
abb <- getSymbols("ABB.NS", src = "yahoo", warnings = F, auto.assign = F)
bob <- getSymbols("BANKBARODA.NS", src = "yahoo", warnings = F, auto.assign = F)
cg <- getSymbols("CROMPTON.NS", src = "yahoo", warnings = F, auto.assign = F)
dabur <- getSymbols("DABUR.NS", src = "yahoo", warnings = F, auto.assign = F)
itc <- getSymbols("ITC.NS", src = "yahoo", warnings = F, auto.assign = F)
nstl <- getSymbols("NESTLEIND.NS", src = "yahoo", warnings = F, auto.assign = F)
ongc <- getSymbols("ONGC.NS", src = "yahoo", warnings = F, auto.assign = F)
tcs <- getSymbols("TCS.NS", src = "yahoo", warnings = F, auto.assign = F)
ril <- getSymbols("RELIANCE.NS", src = "yahoo", warnings = F, auto.assign = F)
pfzr <- getSymbols("PFIZER.NS", src = "yahoo", warnings = F, auto.assign = F)
```

<p>&nbsp;</p>

#### <span style = "color:Green">1. We calculate the monthly returns for the stock and then plot the portfolio of the stock returns</span>
```{r include=FALSE}
stockname =  list(abb, bob, cg, dabur, itc, nstl, ongc, tcs, ril, pfzr)
year = 2008
returns = list()
n = length(stockname)
for(i in 1:n)
  {
  returns[[i]] = periodReturn(stockname[[i]], period = "monthly", 
                            subset = paste(year,"::", sep=""),
                       type = 'log')
  if(i==2){merged_returns <- merge(returns[[i-1]], returns[[i]], all=F)}
  if(i>2){merged_returns <- merge(merged_returns, returns[[i]], all=F)}
}
names = c('ABB', 'BankofBaroda', 'Crompton', 'Dabur' , 'ITC', 'Nestle', 'ONGC', 'TCS', 'RIL', 'Pfizer')
for(i in 1:length(names)){
  colnames(merged_returns)[i] <- names[i]
}

```


```{r echo = FALSE, out.width= "115%"}
dygraph(merged_returns, main = "Comparison of various stocks in the portfolio") %>% 
  dyAxis("y", label = "%") %>% 
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set1"))
```

<p>&nbsp;</p>

#### <span style = "color:Green">2. Calculate the portfolio returns</span>
```{r echo=FALSE, out.width="115%"}
stock_value = c(38656.80, 19582.2, 54844.95,42050, 100698, 49184, 19387, 73637, 69252, 83600)
total_portfolio_value = sum(stock_value)
weight<- stock_value/total_portfolio_value

portfolio_return <- Return.portfolio(merged_returns, weights = weight)

dygraph(portfolio_return, main = "Portfolio return") %>% 
  dyAxis("y", label = "%")
```

<p>&nbsp;</p>

#### <span style = "color:Green">3. Check the portfolio return for Rs.1 invested</span>
```{r echo = FALSE, out.width= "115%"}
portfolio_return_one <- Return.portfolio(merged_returns, weights = weight,wealth.index = TRUE)

dygraph(portfolio_return_one, main = "Portfolio return for Rs. 1 invested") %>% 
  dyAxis("y", label = "%")
```

<p>&nbsp;</p>

#### <span style = "color:Green">4. Calculating the Sharpe ratios for the portfolio as well as each of the stocks</span>
```{r echo = FALSE}
sharpe_ratio <- round(SharpeRatio(portfolio_return, Rf = 0.0647), 4)
cat("The Sharpe Ratio associated with the portfolio is:", sharpe_ratio[1,])
```
```{r echo = FALSE, message=FALSE}
for(i in 1:length(returns))
{
  na.omit(returns[[i]])
  one=list()
  one[[i]] <- na.omit(returns[[i]])
  s1<- round(SharpeRatio(one[[i]], Rf = 0.0647, p = 0.95),4)
  cat(paste("Sharpe Ratio of Stock ",i,sep=" "), ":", s1[1,],"\n")
  }

```

<p>&nbsp;</p>

#### <span style = "color:Green">5. The semi-deviation or the variability of the return below the mean return is:</span>
```{r echo = FALSE}
t(SemiDeviation(merged_returns))
```

<p>&nbsp;</p>

#### <span style = "color:Green">6. Value at risk or the largest loss the portfolio can take within the next quarter with a 95% probability is:</span>

```{r echo = FALSE}
t(VaR(merged_returns, p = 0.95))
```
 
<p>&nbsp;</p>

#### <span style = "color:Green">7. The expected shortfall or the average of all losses greater than or equal to VaR</span>

```{r echo = FALSE}
t(ES(merged_returns, p = 0.95))
```
  
 
<p>&nbsp;</p>  
  
<ol><span style = "color:blue"><h4>The conclusion of the above analysis elucidates the following facts:</h4></span>
  <li><span style = "color:red">The graphs, Sharpe ratios and semideviation values are indicative of negative returns</span></li>
  <li><span style = "color:red">The negative shortfall is indicative of a very risky portfolio</span></li>
  <li><span style = "color:red">The worst of this portfolio may about to come as the markets plummet more and the volatility increases due to covid</span></li>
</ol>

<p>&nbsp;</p>

<ol><span style = "color:blue"><h4>The recommendations for the portfolio are:</h4></span>
  <li><span style = "color:green">For short to medium term returns, a Swedroe rebalancing strategy is recommended rather than a Buy & hold strategy</span></li>
</ol>
