---
title: "Stock analysis using Quantmod"
author: "Manik Hindwan"
date: "25 May 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(TTR)
library(quantmod)
library(PerformanceAnalytics)
library(RColorBrewer)
library(tseries)
library(lubridate)
library(Quandl)
library(dygraphs)
Quandl.api_key("zrcB2Ejv9UmvhPCUsy2_")
options("getSymbols.yahoo.warning"=FALSE)
```

# Read the TESLA stock data
```{r}
tsla = getSymbols("TSLA", auto.assign = FALSE, warnings = F)
tsla_daily <- dailyReturn(Ad(tsla))
plot(tsla_daily)
```

# Let us get the adjusted daily return of facebook stock
```{r}
fb <- getSymbols("FB", auto.assign = F)
fb_daily <- dailyReturn(Ad(fb))
head(fb_daily)
```

# Now transforming the data into monthly returns
```{r}
start_year = 2010
tsla_monthly <- periodReturn(tsla, period = "monthly", 
                             subset = paste(start_year, "::", sep = ""),
                             type = 'log') 
colnames(tsla_monthly) <- as.character('TSLA_returns')
fb_monthly <- periodReturn(fb, period = "monthly", 
                           subset = paste(start_year,"::", sep=""),
                           type= 'log') 
colnames(fb_monthly) <- as.character('FB_returns')
```

# Merging the above data 
```{r}
merged_returns <- merge(tsla_monthly, fb_monthly, all = F)
```

# We will now plot the portfolio returns using dygraph
```{r}
dygraph(merged_returns, main = "Tesla vs Facebook monthly returns") %>% 
  dyAxis("y", label = "%") %>% 
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2"))
```

# Now allocating weights to the portfolio. Weight means the amount of stock 
# owned / Total value of the portfolio
# Suppose I own $4000 worth of facebook stock and $6000 worth of Tesla's
# So my weights are Wfb = 0.4 and Wtsla = 0.6

```{r}
w = c(0.4,0.6)
portfolio_monthly_returns <- Return.portfolio(merged_returns, weights = w)
```

# Charting the portfolio monthly returns
```{r}
dygraph(portfolio_monthly_returns, main = "Portfolio monthly returns") %>% 
  dyAxis("y", label = "%")
```

# Now calculating portfolio monthly returns for $1 invested in this portfolio
```{r}
dollar_growth <- Return.portfolio(merged_returns, weights = w,
                                  wealth.index = T)
dygraph(dollar_growth, main = "How $1 has grown in this portfolio") %>% 
  dyAxis("y", label = "%")
                                  
```

# Now we will calculate the Sharpe ratio which is excess return per unit volatility
```{r}
sharpe_ratio <- round(SharpeRatio(portfolio_monthly_returns, Rf = 0.0003),4)
cat("The sharpe ratio is:", sharpe_ratio[1,])
```

